---
title: 'Motor Trends : Automatic or Manual transmission?'
author: "Yao-Jen Kuo"
date: "Sunday, October 25, 2015"
output:
  html_document:
    toc: false
    number_sections: true
    theme: united
    highlight: tango
---

# Executive Summary

You work for *Motor Trend*, a magazine about the automobile industry. Looking at a data set of a collection of cars, they are interested in exploring the relationship between a set of variables and miles per gallon (MPG) (outcome). They are particularly interested in the following two questions:

* Is an automatic or manual transmission better for MPG?
* Quantify the MPG difference between automatic and manual transmissions

In short, the purpose of this analysis is to find if there is any relationship between a set of variables and MPG.

# Data Management

Factor some numeric variables at the beginning.

```{r}
data(mtcars)
mtcars$cyl <- factor(mtcars$cyl)
mtcars$vs <- factor(mtcars$vs)
mtcars$am <- factor(mtcars$am)
mtcars$gear <- factor(mtcars$gear)
mtcars$carb <- factor(mtcars$carb)
```

# Exploratory Analysis

In *Figure 1* the boxplot suggests a significant difference on fuel consumption between automatic and manual transmission cars. So can we use only transmission type to predict MPG as an univariate linear model?

```{r}
fitUnivariate <- lm(mpg ~ am, data=mtcars)
round(summary(fitUnivariate)$r.squared*100, digits=2)
```

The model explains only **35.98%** of the MPG variation. In *Figure 2* the pairs graph shows that several variables have high correlation with MPG.

# Regression Analysis

Therefore, let us build an initial model using all variables and then using stepwise selection for the best predictors.

```{r}
fitMultivariate <- lm(mpg ~ ., data=mtcars)
fitStepwise <- step(fitMultivariate, direction="both", trace=0)
round(summary(fitStepwise)$r.squared*100, digits=2)#R-squared
summary(fitStepwise)$coef[6,"Pr(>|t|)"]#alpha
```

The final model contains 4 predictors including cyl(number of cylinders), hp(horsepower), weight(weight) and am(transmission type). This model explains **86.59%** of the MPG variation. The transmission has no effect on the fuel consumption since **$\alpha$=0.2064597>0.05**.

## Residual Analysis and Diagnostics

According to *Figure 3* we can verify the following underlying assumptions:

1. The Residuals vs Fitted plot shows no consistent pattern.
2. The Normal Q-Q plot indicates that the residuals are normally.
3. The Scale-Location plot confirms the constant variance assumption.
4. The Residuals vs Leverage confirms that no outliers are present.

# Conclusion

```{r}
c(abs(fitStepwise$coef[2]), abs(fitStepwise$coef[3]), 
  abs(fitStepwise$coef[4]), abs(fitStepwise$coef[5]))
```

1. If a car has 6 or 8 cylinders, everything else same, the MPG decreases by **3.031344** and **2.163675**, respectively.
2. One unit of increase on gross horsepower, everything else same, results a decrease of **0.03210943** on MPG.
3. 1,000 lb increase on the weight of a car, everything else same, results a decrease of **2.496829** on MPG.
4. This analysis was not able to find significant link between the transmission type and fuel consumption. It is less likely that driving a manual car will save you any money on gasoline.

# Appendix

## Figure 1

Boxplot of MPG vs. Transmission

```{r, echo=FALSE, warning=FALSE, message=FALSE}
library(ggplot2)
```

```{r, fig.height=3}
ggplot(mtcars, aes(x=am, y=mpg, fill=am)) +
  geom_boxplot() +
  xlab("Transmission type") +
  ylab("MPG")
```

## Figure 2

Pairs Graph of `mtcars`

```{r, fig.height=7}
pairs(mtcars, panel=panel.smooth, main="Pair Graph of mtcars")
```

## Figure 3

Residual Analysis and Diagnostics

```{r, fig.height=5}
par(mfrow = c(2,2))
plot(fitStepwise)
```