---
title: "Quiz3"
author: "Yao-Jen Kuo"
date: "Sunday, October 25, 2015"
output:
  html_document:
    theme: united
    toc: true
    toc_depth: 2
    highlight: tango
    fig_width: 9
    fig_height: 5
    fig_caption: false
---

# Regression Models At Coursera

## Quiz 3

### Question 1

Consider the `mtcars` data set. Fit a model with mpg as the outcome that includes number of cylinders as a factor variable and weight as confounder. Give the adjusted estimate for the expected change in mpg comparing 8 cylinders to 4.

```{r}
data(mtcars)
fit <- lm(mpg ~ factor(cyl) + wt, mtcars)
summary(fit)$coef[3, 1]
```

Answer  | Options
------- | -------
|  | -3.206 
V  | -6.071
|  | 33.991
|  | -4.256

### Question 2

Consider the `mtcars` data set. Fit a model with mpg as the outcome that includes number of cylinders as a factor variable and weight as a possible confounding variable. Compare the effect of 8 versus 4 cylinders on mpg for the adjusted and unadjusted by weight models. Here, adjusted means including the weight variable as a term in the regression model and unadjusted means the model without weight included. What can be said about the effect comparing 8 and 4 cylinders after looking at models with and without weight included?

```{r}
summary(fit)$coef
fitUnadjusted <- lm(mpg ~ factor(cyl), mtcars)
summary(fitUnadjusted)$coef
```

Answer  | Options
------- | -------
|  | Including or excluding weight does not appear to change anything regarding the estimated impact of number of cylinders on mpg.
|  | Within a given weight, 8 cylinder vehicles have an expected 12 mpg drop in fuel efficiency.
V  | Holding weight constant, cylinder appears to have less of an impact on mpg than if weight is disregarded.
|  | Holding weight constant, cylinder appears to have more of an impact on mpg than if weight is disregarded.

### Question 3

Consider the `mtcars` data set. Fit a model with mpg as the outcome that considers number of cylinders as a factor variable and weight as confounder. Now fit a second model with mpg as the outcome model that considers the interaction between number of cylinders (as a factor variable) and weight. Give the P-value for the likelihood ratio test comparing the two models and suggest a model using 0.05 as a type I error rate significance benchmark.

```{r, message=FALSE, warning=FALSE}
fitNonInteraction <- lm(mpg ~ factor(cyl) + wt, mtcars)
summary(fitNonInteraction)$adj.r.squared
fitInteraction <- lm(mpg ~ factor(cyl) + wt + factor(cyl):wt, mtcars)
summary(fitInteraction)$adj.r.squared
library(lmtest)
lrtest(fitInteraction, fitNonInteraction)
```

Answer  | Options
------- | -------
|  | The P-value is larger than 0.05. So, according to our criterion, we would fail to reject, which suggests that the interaction terms is necessary.
|  | The P-value is small (less than 0.05). So, according to our criterion, we reject, which suggests that the interaction term is necessary
|  | The P-value is small (less than 0.05). So, according to our criterion, we reject, which suggests that the interaction term is not necessary.
|  | The P-value is small (less than 0.05). Thus it is surely true that there is no interaction term in the true model.
|  | The P-value is small (less than 0.05). Thus it is surely true that there is an interaction term in the true model.
V  | The P-value is larger than 0.05. So, according to our criterion, we would fail to reject, which suggests that the interaction terms may not be necessary.

### Question 4

Consider the `mtcars` data set. Fit a model with mpg as the outcome that includes number of cylinders as a factor variable and weight inlcuded in the model as

```{r}
fit <- lm(mpg ~ I(wt * 0.5) + factor(cyl), data = mtcars)
```

How is the wt coefficient interpretted?

```{r}
summary(fit)$coef
```

Answer  | Options
------- | -------
|  | The estimated expected change in MPG per one ton increase in weight.
|  | The estimated expected change in MPG per half ton increase in weight for for a specific number of cylinders (4, 6, 8).
|  | The estimated expected change in MPG per half ton increase in weight.
V  | The estimated expected change in MPG per one ton increase in weight for a specific number of cylinders (4, 6, 8).
|  | The estimated expected change in MPG per half ton increase in weight for the average number of cylinders.

### Question 5

Consider the following data set

```{r}
x <- c(0.586, 0.166, -0.042, -0.614, 11.72)
y <- c(0.549, -0.026, -0.127, -0.751, 1.344)
```

Give the hat diagonal for the most influential point

```{r}
fit <- lm(y ~ x)
max(hatvalues(fit))
```

Answer  | Options
------- | -------
V  | 0.9946
|  | 0.2804
|  | 0.2287
|  | 0.2025

### Question 6

Consider the following data set

```{r}
x <- c(0.586, 0.166, -0.042, -0.614, 11.72)
y <- c(0.549, -0.026, -0.127, -0.751, 1.344)
```

Give the slope dfbeta for the point with the highest hat value.

```{r}
influence.measures(fit)$infmat[5, 'dfb.x']
```

Answer  | Options
------- | -------
|  | 0.673
|  | -.00134
|  | -0.378
V  | -134

### Question 7

Consider a regression relationship between Y and X with and without adjustment for a third variable Z. Which of the following is true about comparing the regression coefficient between Y and X with and without adjustment for Z.

Answer  | Options
------- | -------
|  | The coefficient can't change sign after adjustment, except for slight numerical pathological cases.
V  | It is possible for the coefficient to reverse sign after adjustment. For example, it can be strongly significant and positive before adjustment and strongly significant and negative after adjustment.
|  | For the the coefficient to change sign, there must be a significant interaction term.
|  | Adjusting for another variable can only attenuate the coefficient toward zero. It can't materially change sign.